\thetitle: Technical Report

### 2023-04-05 casestudies.tex
cut to save space
back on 22 pages

@@

\begin{wrapfigure}[13]{r}{0.138\textwidth}
\includegraphics[scale=.68]{graphics/ai-casestudy.pdf}
\end{wrapfigure}

@@

The next two families then extend \lsti{ImpGAI}.
Family \lsti{ImpTI} (\textasciitilde200~LOC) is an abstract
interpreter that does type inference~\cite{cousot1997types}.
Family \lsti{ImpCP} (\textasciitilde300~LOC) extends the abstract syntax
with natural-number arithmetic,
and further binds the generic abstract interpreter to perform constant propagation.
%
%An alternative to \Lang would be to define \lsti{ImpGAI} as a functor parameterized
%by the abstract domain and such. But it would prevent \lsti{ImpCP} from reusing
%the code and proofs in \lsti{ImpGAI}, because \lsti{ImpCP} involves extending
%inductive types with new constructors.

@@

We note that \Lang cannot yet allow the expression of two derived abstract
interpreters nested within the same family.
Work on nested inheritance~\cite{ncm2004,zm2017} points to a direction
to further increase the expressive power of our language design.

>>>>

\begin{wrapfigure}[13]{r}{0.132\textwidth}
\includegraphics[scale=.66]{graphics/ai-casestudy.pdf}
\end{wrapfigure}

@@

@@

The next two families both extend \lsti{ImpGAI}.
Family \lsti{ImpTI} (\textasciitilde200~LOC) is an abstract
interpreter doing type inference~\cite{cousot1997types}.
Family \lsti{ImpCP} (\textasciitilde300~LOC) extends the abstract syntax
with natural-number arithmetic,
and further binds the generic abstract interpreter to perform constant propagation.
%
%An alternative to \Lang would be to define \lsti{ImpGAI} as a functor parameterized
%by the abstract domain and such. But it would prevent \lsti{ImpCP} from reusing
%the code and proofs in \lsti{ImpGAI}, because \lsti{ImpCP} involves extending
%inductive types with new constructors.

@@

%We note that \Lang cannot yet allow the expression of two derived abstract
%interpreters nested within the same family.
%Work on nested inheritance~\cite{ncm2004,zm2017} points to a direction
%to further increase the expressive power of our language design.

### 2023-04-05 related-work.tex
back on 22 pages

\citet{boite2004proof} addresses proof reuse specifically in response
to inductive types extended with new constructors. Proof reuse is
via a tactic that adapts the original proof to the extended inductive
type while generating proof obligations, so rechecking of proof terms is
entailed.
The design requires distinct names for a base inductive type and its
extensions (including distinct names for constructors), while family
polymorphism in our approach allows names to be late bound.

>>>>

\citet{boite2004proof} addresses proof reuse specifically in response
to inductive types extended with new constructors. Proof reuse is
via a tactic that adapts the original proof to the extended inductive
type while generating proof obligations, so rechecking of proof terms is
entailed.
The design requires distinct names for a base inductive type and its
extensions (including distinct names for constructors), while \Lang allows names to be late bound.
